%!TeX program = pdflatex
% Zixing Jiang's Curriculum Vitae
% Email: zxjiang@surgery.cuhk.edu.hk
% Web: https://zixingjiang.com/
% Repo: https://github.com/zixingjiang/cv

\documentclass[11pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{setspace} % custom line spacing (should load this before hyperref)
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage[dvipsnames]{xcolor}
\usepackage[fixed]{fontawesome5}
\usepackage{textcase}



% what is your name?
\newcommand{\myname}{JIANG Zixing}

% select default typefaces
\usepackage{ebgaramond} % document's serif font
\usepackage{tgheros}  % document's sans serif font

%\usepackage{ebgaramond} % document's serif typeface
%\usepackage{tgheros}    % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\MakeUppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{
  left=1.0in,
  right=1.0in,
  top=0.8in,
  bottom=1.2in
}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.9}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
			\setlength{\parskip}{0em}
			\setlength{\itemsep}{\listitemspace}
			\setlength{\parsep}{\listitemspace}}}
	{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
	labelindent=0em,
	topsep=0em,
	partopsep=0em,
	itemsep=\listitemspace,
	parsep=\listitemspace,
	font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
	colorlinks  = true,
	urlcolor    = Blue,
	citecolor   = blue,
	linkcolor   = Blue,
	pdfauthor   = {\myname},
	pdftitle    = {\myname: Curriculum Vitae},
	pdfsubject  = {Curriculum Vitae},
	pdfpagemode = UseNone
}


\usepackage[multiple, hang, flushmargin, stable]{footmisc}
\usepackage{fnpct}
\addtolength{\skip\footins}{1.5pc plus 5pt}
\renewcommand\thefootnote{\textcolor{Blue}{\arabic{footnote}}}


\usepackage{fancyhdr}
\usepackage{lastpage}

% Custom footer for the first page
\fancypagestyle{firstpagefooter}{
	\fancyhf{}
	\fancyfoot[R]{\monthyeardate\today}
	\fancyfoot[C]{\thepage ~of \pageref{LastPage}}
	\renewcommand{\headrulewidth}{0pt}
	\renewcommand{\footrulewidth}{0pt}
}

% Custom footer for the rest of the pages
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\thepage ~of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}

\begin{document}
	\thispagestyle{firstpagefooter}
	\raggedright{}
	
% display your name as the document title
\namefont{\myname}
	
% affiliation and contact info blocks
\vspace{1em}
\begin{minipage}[t]{0.700\textwidth}
	% current primary affiliation, left-aligned
	M.Phil. Student, Department of Surgery\\
	Faculty of Medicine, The Chinese University of Hong Kong\\
	Sha Tin, N.T., Hong Kong, China
\end{minipage}
\hfil
\begin{minipage}[t]{0.295\textwidth}
	% contact info details, right-aligned
	\flushright{}
	\href{mailto:zxjiang@surgery.cuhk.edu.hk}{zxjiang@surgery.cuhk.edu.hk} \\
	+852 5954 9660 \\
	\href{https://zixingjiang.com}{https://zixingjiang.com}\\
\end{minipage}
	
\section*{Education}
\begin{tablist}
	\item[M.Phil.]  \tab{}Surgery, The Chinese University of Hong Kong (CUHK), China, In progress 2024--\\
	\item[B.Eng.]  \tab{}Electronic Information Engineering, \textit{First-Class Honors}, CUHK-Shenzhen, China, 2023
	
	\textit{Final Year Project: Control of the Multi-Joint Manipulator for Grasping on Water Surface, supervised by \href{https://sse.cuhk.edu.cn/en/faculty/qianhuihuan}{Prof. QIAN Huihuan}.}
\end{tablist}
	

\section*{Experience}
\begin{tablist}	
	\item[2023--24]   \tab{}Department of Surgery, CUHK \hfill Hong Kong, China
	
	\textit{Research Assistant, Advanced Bio-Medical Robotics Lab} \hfill \textit{Nov. 2023 -- Jul. 2024}
		
	\item[2020--23]   \tab{}Robotics \& AI Lab (RAIL), CUHK-Shenzhen \hfill Shenzhen, China
	
	\textit{Research Intern, SUN Group (surgical robots and medical devices)} \hfill \textit{Feb. 2023 -- Aug. 2023}\\
	\textit{Research Intern, Advanced Marine Robotics Group} \hfill \textit{Sept. 2020 -- Feb. 2023}
\end{tablist}
	
\section*{Research Interests}
\begin{itemize}
	\item Robotics; Medical Robotics; Surgical Robotics
	\item Image-Guided Robotic Interventions
	\item Robot-Assisted Imaging
\end{itemize}
	
\section*{Selected Projects}
\begin{tablist}
	
	\item[2024--] \tab Robotic Ultrasound-Guided Prostate Biopsy

	\textit{Ongoing research project at CUHK, supervised by  \href{https://www.surgery.cuhk.edu.hk/profile.asp?alias=zli}{Prof. LI Zheng} and \href{https://www.surgery.cuhk.edu.hk/profile.asp?alias=peterchiu}{Prof. CHIU Ka Feng Peter}.}
	
	\textit{Developing an ultrasound image-guided needle navigation program for a prostate biopsy robot and assisting in related clinical tests.}
	
	\item[2023--24] \tab Autonomous Robotic Lung Ultrasound
	
	\textit{Research project at CUHK, supervised by \href{https://www.surgery.cuhk.edu.hk/profile.asp?alias=zli}{Prof. LI Zheng} and \href{https://www.cse.cuhk.edu.hk/people/faculty/pheng-ann-heng/}{Prof. HENG Pheng Ann}.}
	
	\emph{Developed a robot prototype for autonomous lung ultrasound and assisted in its preclinical validations.}

	\item[2020--23] \tab Manipulator-Assisted UAV Landing System for USV
	
	\textit{Research project at CUHK-Shenzhen, supervised by \href{https://sse.cuhk.edu.cn/en/faculty/qianhuihuan}{Prof. QIAN Huihuan}.}
	
	\emph{Assisted in developing end-effectors and motion planning algorithms for a manipulator-assisted system that facilitates unmanned aerial vehicles (UAVs) landing on unmanned surface vehicles (USVs) in the presence of wave disturbances. }	
\end{tablist}
	
\section*{Publications\protect\footnote{\label{authorship}\NoCaseChange{Notations: $^*$ co-first authors, $^\dagger$ corresponding authors.}}}
\subsection*{Journal Articles}
\begin{tablist}
%	\item[2025] \tab Y. Hu, Y. Song, \textbf{Z. Jiang}, L. Lei, X. Luo, K. Alois, P.-A. Heng, and Z. Li$^\dagger$, ``Deep Imitation Learning for Fully Autonomous Robotic Lung Ultrasound Scanning'', in \textit{IEEE Transactions on Robotics (T-RO)}, 2025
%	
%	\item[2025] \tab \textbf{Z. Jiang}, Y. Hu, and Z. Li$^\dagger$, ``Universal Hand-Eye Calibration for Robotic and Freehand Ultrasound: A Conic Section Approach'', in \textit{IEEE Robotics and Automation Letters (RA-L)}, 2025
%	
%	
	\item[2025]	 \tab{}L. Lei$^*$, Y. Hu$^*$, \textbf{Z. Jiang}$^*$, J. Miao, X. Luo, Y. Zhang, Q. Wang, S. Wang$^\dagger$, Z. Li$^\dagger$, and P.-A. Heng, ``Towards Lung Ultrasound Automation: Fully Automonous Robotic Longitudinal and Transverse Scans Along Intercostal Spaces,'' in \textit{IEEE Transactions on Medical Robotics and Bionics (T-MRB)}, Early Access, 2025, doi: \href{https://doi.org/10.1109/TMRB.2025.3550663}{10.1109/TMRB.2025.3550663}.
	
	\item[2024]  \tab{}R. Xu, \textbf{Z. Jiang}, B. Liu, Y. Wang, and H. Qian$^\dagger$, ``Confidence-Aware Object Capture for a Manipulator Subject to Floating-Base Disturbances,'' in \textit{IEEE Transactions on Robotics (T-RO)}, vol. 40, pp. 4396-4413, 2024,  doi: \href{https://doi.org/10.1109/TRO.2024.3463476}{10.1109/TRO.2024.3463476}.
\end{tablist}
	
\subsection*{Conference Papers}
\begin{tablist}
%	\item[2025] \tab X. Luo, \textbf{Z. Jiang}, M. C. Lei, Y. Xian, Y. Hu, A. Dong, P. K. F. Chiu, Y. Liu, and Z. Li$^\dagger$, ``Design and Geometry-Aware Planning of a Novel Probe-Scanning Manipulator with RCM Constraint'', \textit{2025 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), Hangzhou, China, 2025}
%	
	
	\item[2023]   \tab{}Y. Jiang, R. Xu, \textbf{Z. Jiang} and H. Qian$^\dagger$, ``Design, Modeling and Control of A Novel USV-Manipulator System,'' \textit{2023 IEEE International Conference on Real-time Computing and Robotics (RCAR)}, Datong, China, 2023, pp. 206-211, doi: \href{https://doi.org/10.1109/RCAR58764.2023.10249802}{ 10.1109/RCAR58764.2023.10249802}.
		
	\item[2022]   \tab{}C. Liu, \textbf{Z. Jiang}, R. Xu, X. Ji, L. Zhang and H. Qian$^\dagger$, ``Design and Optimization of a Magnetic Catcher for UAV Landing on Disturbed Aquatic Surface Platforms,'' \textit{2022 International Conference on Robotics and Automation (ICRA)}, Philadelphia, PA, USA, 2022, pp. 1162-1168, doi: \href{https://doi.org/10.1109/ICRA46639.2022.9812270}{ 10.1109/ICRA46639.2022.9812270}.
\end{tablist}
	
\subsection*{Patents}
\begin{tablist}	
	\item[2024]   \tab{}C. Liu, Z. Cao, \textbf{Z. Jiang}, R. Xu, X. Ji, and H. Qian, ``Unmanned aerial vehicle landing system, landing method and storage medium,'' Chinese patent \href{https://patents.google.com/patent/CN115167522A/en?oq=CN115167522A}{CN115167522B}, granted Nov. 1, 2024.	
		
	\item[2023]   \tab{}\textbf{Z. Jiang}, X. Ji, C. Liu, and H. Qian, ``Four-wing flapping wing micro water surface aircraft and flight method,'' Chinese patent \href{https://patents.google.com/patent/CN114889821B/en?oq=CN114889821B}{CN114889821B}, granted Feb. 24, 2023.
		
	\item[2022]   \tab{}X. Ji, Z. Song, \textbf{Z. Jiang}, and H. Qian, ``Flapping wing mechanism and miniature water surface flapping wing aircraft,'' Chinese patent \href{https://patents.google.com/patent/CN217320745U/en?oq=CN217320745U}{CN217320745U}, granted Aug. 30, 2022.  
		
	\item[2022]   \tab{}X. Ji, Z. Song, \textbf{Z. Jiang}, and H. Qian, ``Flapping wing mechanism based on double cranks and micro water surface flapping wing aircraft,'' Chinese patent \href{https://patents.google.com/patent/CN217320744U/en?oq=CN217320744U}{CN217320744U}, granted Aug. 30, 2022.  
\end{tablist}
	
	
	
\section*{Abstracts \& Presentations}
\begin{tablist}	
	\item[2024] \tab \textbf{Z. Jiang}, Y. Hu, X. Luo, J. Miao, Y. Zhang, L. Lei, S. Wang, P.-A. Heng, and Z. Li, ``A Collaborative Robotic System with In-Plane Orientation Adjustment for Lung Ultrasonography,'' presented at workshop \textit{Autonomy in Robotic Surgery: State of the art, technical and regulatory challenges for clinical application}, 2024 IEEE International Conference on Robotics and Automation (ICRA), Yokohama, Japan, May 13, 2024.
\end{tablist}
	
\section*{Open Source Contributions}
\subsection*{Author \& Maintainer}
\begin{itemize}
	\item \texttt{ndi\_ros2\_driver} (\href{https://github.com/zixingjiang/ndi_ros2_driver}{https://github.com/zixingjiang/ndi\_ros2\_driver})
	
	\textit{ROS2-control integration for Northern Digital Inc. (NDI) electromagnetic tracking and optical navigation systems.}
	
	\item \texttt{minimal\_handeye\_ros2} (\href{https://github.com/zixingjiang/minimal_handeye_ros2}{https://github.com/zixingjiang/minimal\_handeye\_ros2})
	
	\textit{A minimal hand-eye calibration node for ROS 2.}
\end{itemize}
\subsection*{Contributor}
\begin{itemize}
	\item \texttt{cartesian\_controllers} (\href{https://github.com/fzi-forschungszentrum-informatik/cartesian_controllers}{https://github.com/fzi-forschungszentrum-informatik/cartesian\_controllers})
	
	\textit{A set of Cartesian controllers for the ROS1 and ROS2-control framework.}
\end{itemize}
	
\section*{Peer Review}
\subsection*{Academic Conferences}
\begin{itemize}
	\item \textit{The IEEE International Conference on Robotics and Automation (ICRA)}
	\item \textit{The IEEE/RSJ International Conference	on Intelligent Robots and Systems (IROS)}
	\item \textit{The IEEE International Conference on Robotics and Biomimetics (ROBIO)}
\end{itemize}
	
\section*{Teaching}
\begin{tablist}
\item[2025] \tab Teaching Assistant, Medical Robotics (BMEG5750), Postgraduate Course, CUHK
\end{tablist}
	
\section*{Leadership}
\begin{tablist}
	\item[2020--22]   \tab President, RAIL Student Robotics Association, CUHK-Shenzhen 
\end{tablist}
	
\section*{Awards}
\begin{tablist}	
%	\item[2025] \tab Finalist (Group), Prof. Charles K. Kao Student Creativity Awards, CUHK
%	
%	\textit{A Novel Robotic System for Minimally Invasive Transperineal Prostate Biopsy with Enhanced Safety.}
%	
	
	\item[2024] \tab Bronze Award (Team), The 14th ``Challenge Cup'' QinChuangYuan Platform National College Students' Entrepreneurship Competition, China

	\textit{ColoMAG: A Magnet-Assisted System for Colorectal Cancer Screening and Early Surgical Treatment.}	

	\item[2023]   \tab School of Science and Engineering Academic Year 2022--23 Dean's List Award, CUHK-Shenzhen
	\item[2021--22]   \tab The 17--19th rounds of  Undergraduate Research Award, CUHK-Shenzhen
	
	\textit{Bio-inspired Robot for Aquatic-Aerial Hybrid Locomotion.}
	
	\item[2020] \tab RoboCom\footnote{RoboCom renamed to RAICOM in 2023.} Robot Developer Competition -- ``Treasure Hunter'' Southern China Regional Competition
	
	\textit{Second Prize (Team) in Semi-Autonomous Robot Palletizing Competition;}
	
	\textit{Third Prize (Team) in Semi-Autonomous Robot Palletizing Timed Race;}
	
	\textit{Third Prize (Team) in Autonomous Robot Palletizing Competition.}
\end{tablist}
	
\section*{Technical Skills}
\begin{tablist}
	\item[Coding] \tab Python, C++, C, MATLAB
	\item[Robotics] \tab Possesses full-stack robotics development experience, with a focus on motion planning and control
	\item[Software] \tab Libraries: ROS, Eigen, NumPy, OpenCV, Open3D, PyTorch\\
	Simulators: Gazebo, CoppeliaSim, SOFA\\
	3D Modeling: SolidWorks, Blender\\
	Miscellaneous: Docker, 3D Slicer
	\item[Hardware] \tab Platforms: Linux, Arduino, Raspberry Pi, STM32, ESP32, FPGA\\
	Robots: Manipulator, Ornithopter, UAV, USV, UGV\\ 
	Sensors: RGB-D Camera, Force/Torque Sensor, Optical Tracker, Electromagnetic Tracker\\
	Interfaces: Haptic Devices, Joysticks\\
	Medical Imaging: Ultrasound
\end{tablist}


\section*{Languages}
\begin{tablist}
	\item[Chinese] \tab Mandarin -- Native
	\item[English] \tab Professional Proficiency
\end{tablist}
\newpage
\section*{References}
\begin{itemize}
	\item \textbf{Prof. LI Zheng} ~{\scriptsize \faEnvelope}\href{mailto:zhengli@cuhk.edu.hk}{zhengli@cuhk.edu.hk}\\
	Associate Professor\\
	Department of Surgery\\
	The Chinese University of Hong Kong
	
	\textit{Relationship: M.Phil. Supervisor.}

	\vspace{1ex}
	
	\item \textbf{Prof. QIAN Huihuan (Alex)} ~{\scriptsize \faEnvelope}\href{mailto:hhqian@cuhk.edu.cn}{hhqian@cuhk.edu.cn}\\
	Associate Professor\\School of Science and Engineering\\The Chinese University of Hong Kong, Shenzhen

	\textit{Relationship: Undergraduate Final Year Project Supervisor.}

\end{itemize}
	
% display today's date as Month Year after a vertical space below the end of the text
\begin{center}
	\vfill
	Last update: \monthyeardate\today; \href{https://zixingjiang.com/cv/}{https://zixingjiang.com/cv/}
\end{center}
	
\end{document}